Commutative Character Sheaves

### 2015-07-24 followup.tex
Fixing some references

As proved in \cite{kim:exhaustion}, many (complex) supercuspidal representations of $p$-adic groups can be built from the generic data of \cite{yu:construction}*{\S 15} and, moreover, that the type of the resulting supercuspidal representations can be constructed directly from the generic data. Let us refer to the types arising in this manner as {\it generic types}.
In this section we show that, after fixing an isomorphism $\CC \approx \EE$, every generic type is geometrizable, in the sense that every part of generic type admits a description as a sheaf, from which the type can be recovered.

Let $K$ be a $p$-adic field. Let $\G$ be a connected reductive linear algebraic group over $K$. A generic datum is a triple $(\vec{\G}, \pi_0, \vec{\phi})$ where: $\vec{\G}$ is a tower of $p$-adic groups $\G^0 \subsetneq \G^1 \subsetneq \cdots \G^d = \G$; $\pi_0$ is a depth-zero representation of $\G^0(F)$, and $\vec{\phi} = (\phi_0, \ldots , \phi_{d-1})$ where $\phi_i : \G^i(K) \to \EEx$ is a quasicharacter (continuous group homomorphism). 
In \cite{yu:smooth}*{\S 10.5}, it is shown that

>>>>

As proved in \cite{kim:07a}, many (complex) supercuspidal representations of $p$-adic groups can be built from the generic data of \cite{yu:01a}*{\S 15} and, moreover, that the type of the resulting supercuspidal representations can be constructed directly from the generic data. Let us refer to the types arising in this manner as {\it generic types}.
In this section we show that, after fixing an isomorphism $\CC \approx \EE$, every generic type is geometrizable, in the sense that every part of generic type admits a description as a sheaf, from which the type can be recovered.

Let $K$ be a $p$-adic field. Let $\G$ be a connected reductive linear algebraic group over $K$. A generic datum is a triple $(\vec{\G}, \pi_0, \vec{\phi})$ where: $\vec{\G}$ is a tower of $p$-adic groups $\G^0 \subsetneq \G^1 \subsetneq \cdots \G^d = \G$; $\pi_0$ is a depth-zero representation of $\G^0(F)$, and $\vec{\phi} = (\phi_0, \ldots , \phi_{d-1})$ where $\phi_i : \G^i(K) \to \EEx$ is a quasicharacter (continuous group homomorphism). 
In \cite{yu:03a}*{\S 10.5}, it is shown that
